\leavevmode\vfill
Thank you to Adam, for not expelling me when I reported a potential security vulnerability in his principles of programming languages' project submission server, but instead inviting me to take his course on software security and inviting me to join ASU's hacking team, the pwndevils.
His course immediately hooked me into the "cybersecurity" world.
It was more game-like than it was course-like, with an actual scoreboard on several of the assignments, which ultimately created the passion I have today for solving security challenges.
From there, Adam gave me the amazing opportunity to do security research with him and serve as a teaching assistant in his software security course.
These experiences have been truly invaluable and absolutely amazing to be a part of.

Thank you to Yan, for showing me that anything can be done the day before it is absolutely necessary, as we worked through the night and early morning at a coffee shop--just before his first class on systems security--to create a challenge infrastructure (which would be hacked by one of the students just hours later).
I remember listening to Yan's talk on angr at DEF CON 23, a couple of years before he joined our lab--and I remember how excited I was when I learned that this legendary hacker might join our lab.
The level of energy and humor that Yan has brought to the lab is truly inspiring.

It has been an absolute blast working with both Adam and Yan, as well as Fish, Tiffany, and the rest of the lab. Our amazing lab is the reason that I continue to do research.
\vfill
